### 2014-07-10 tex/proofs.tex
fixed some minor typos

\begin{definition}
\label{exact}
A state $s$ is \textbf{exact} with respect to a transition relation, $\rightarrow_\phi$, an initial state, $s_0$, and specific control flow path, $\pi_n$, if and only if it is congruent to the set of feasible state set:
$$ s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi)$$
\end{definition}

@@

\begin{lemma}
If there is some access path $\sigma$ in state $s_s$ such that $\mathbb{s}(\phi_\sigma \wedge \phi_s)$, then $\sigma \sqsubset$  
\end{lemma}
\begin{proof}
\end{proof}

>>>>

\begin{definition}
\label{exact}
A state $s$ is \textbf{exact} with respect to a transition relation, $\rightarrow_\phi$, an initial state, $s_0$, and specific control flow path, $\pi_n$, if and only if it is congruent to the set of feasible state set:
$$ s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$$
\end{definition}

@@

\begin{lemma}
If there is some access path $\Gamma$ in state $s_s$ such that $\mathbb{S}(\phi_\sigma \wedge \phi_s)$, then $\sigma \sqsubset$  
\end{lemma}
\begin{proof}
\end{proof}
